>-

### 2023-12-07 manuscript/appendix.qmd
Finish appendix

---
title: >-
  Online appendix for "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
short-title: 'Online appendix for "Enforcing Boundaries"'
date: "2023-12-07"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.bib
link-citations: true
crossref: 
  tbl-title: Appendix Table
  fig-title: Appendix Figure
---

@@

# Appendix

@@

## Coding rules for issue ares

Author 1 assigned each organization to one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases

1. Education vs. Charity
If charitable activities are all education related, e.g. building schools, donating education facilities and books, coded as education
If the aids provided include other community support, e.g. building bridges, roads, medical facilities, coded as charity

2. Economy and trade vs. Industry association
If the trade promoted is focused on a particular industry (poultry, grains etc.), coded as industry association

3. Arts and culture 
Include sports organizations too.

4. Industry association vs. health, science and technology, arts and culture

There are professional association on health providers and certain techniques. Coded as health, science & technology if work areas go beyond serving members only: for example conducting activities of promoting and training about certain techniques.

If specialized association only serves the member companies: coded as industry associations

5. Health vs. Charity 
If only providing medical aids to underprivileged communities, not building schools etc., coded as health

6. Charity vs. General 
If multiple work, e.g., poverty alleviation, education, health can be encompassed by Charity and humanitarian, then the former

7. Multiple ROs are coded based on the overall work area spans of the INGO, not the specific RO, so to ensure the issue area coding is consistent across ROs

## Modeling details

We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-1 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate the model We simulate 4 MCMC chains with 2,000 draws in each chain, 1,000 of which are used for warmup, resulting in 4,000 (1,000 × 4) draws per model parameter. We assess convergence with visual inspection, and all chains converge. Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics—as well as our code and data—are available `ANONYMIZED_URL`.

TODO: Model definition and priors like NVSQ paper

>>>>

---
title: >-
  Online appendix for "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
short-title: 'Online appendix for "Enforcing Boundaries"'
date: "2023-12-07"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.bib
link-citations: true
---

@@

```{r libraries-data}
library(tidyverse)
library(scales)
library(modelsummary)
library(gt)
library(targets)

# Generated via random.org
set.seed(8511)

# Targets stuff
tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

tar_load(c(models_tbl))

# Plotting and modelsummary functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ongo())
set_annotation_fonts()
```

# Model details and results

We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-1 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate our ordered Beta regression models [@Kubinec:2022]. We simulate 4 MCMC chains with 2,000 draws in each chain, 1,000 of which are used for warmup, resulting in 4,000 (1,000 × 4) draws per model parameter. We assess convergence with visual inspection, and all chains converge. Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics—as well as our code and data—are available `ANONYMIZED_URL`. We include the formal definition and priors for our model below.

@@

\newpage

::: {#tbl-coefs-orig}

\footnotesize

```{r}
#| label: table-coefs-orig
#| include: true

notes <- c(
  "Estimates are median posterior log odds from ordered Beta regression models;",
  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
)

modelsummary(
  models_tbl$msl, 
  estimate = "{estimate}",
  statistic = "[{conf.low}, {conf.high}]",
  fmt = fmt_significant(2),
  coef_map = models_tbl$nice_coefs,
  output = "gt"
) |> 
  opts_theme() |>
  tab_footnote(
    footnote = paste(notes, collapse = " ")
  ) %>%
  opts_theme() |>
  tab_options(
    quarto.disable_processing = TRUE
  )
```

Complete model coefficients

:::

\clearpage

# Coding rules for issue ares

Author 1 assigned each organization to one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases. Organizations with multiple ROs are coded based on the overall issue area of the INGO, not the specific RO, so to ensure the issue area coding is consistent across ROs.

We followed these rules for categorizing INGOs' stated missions into issue areas:

- **Education vs. Charity and humanitarian**: If charitable activities are all education related (e.g., building schools, donating education facilities and books), code as *Education*. If activities include other community support (e.g., building bridges, roads, medical facilities), code as *Charity and humanitarian*.
- **Economy and trade vs. Industry association**: If the trade promoted is focused on a particular industry (e.g., poultry, grains, etc.), code as *Industry association*.
- **Arts and culture**: Include sports organizations.
- **Industry association vs. Health & Science and technology & Arts and culture**: There are professional associations for health providers, scientific associations, and artistic industries. If activities go beyond only serving members only, code as *Health* or *Science and technology* or *Arts and culture*; if activities are limited to member-only service, code as *Industry association*.
- **Health vs. Charity and humanitarian**: If activities only provide medical assistance to underprivileged communities, code as *Health*.
- **Charity and humanitarian vs. General**: If there are overlapping issue areas (e.g., poverty alleviation, education, health), code as *General*, then code the apparent primary issue area as a second work area.

# References
